Conditions for $d$-local-connectedness of boundaries of hyperbolic groups

### 2020-01-22 paper.tex
Wrote down a S condition

In this section we introduce a new condition that a hyperbolic group might
satisfy.

\begin{definition}
  We say that $G$ satisfies $\S_M$ if there exists $k$ such that for any $n$
  sufficiently large and any affine map $f\from \boundary\Delta^2$ \todo{Do
  this}
\end{definition}

>>>>

We now introduce a new condition, which should be thought of as a version of
$\ddag_M$ one dimension higher.

\begin{definition}
  We say that $G$ satisfies $\S_M$ if there exists $k$ such that for any $n$
  sufficiently large and any simplicial map $f\from \sd^M\boundary\Delta^2 \to
  K_n$ that is a simplicial approximation to a map that factors through
  $p^\infty_n \from \boundary G \to K_n$, $f$ admits an extension to $\Delta^2$
  that is affine on $\sd^k \Delta^2$.
\end{definition}
